
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
%\usepackage{fontawesome}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
\vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
	\textbf{#1}{: #2 \vspace{-2pt}}
}
}

\newcommand{\resumeSubheading}[4]{
\vspace{-1pt}\item
\begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{#1} & #2 \\
	\textit{\small#3} & \textit{\small #4} \\
\end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%% CV STARTS HERE %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------


\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://www.linkedin.com/in/musharraf-rao}{\Large  M.Musharraf Naseem}}
\end{tabular*}
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
	\textbf{\href{https://www.linkedin.com/in/musharraf-rao}{\Large}} & \tiny{\href{mailto:fast.musharraf@gmail.com}{fast.musharraf@gmail.com}},
	\tiny{\href{https://github.com/RaoMusharraf}{https://github.com/RaoMusharraf}}, \tiny{+92 3020321360},
	\tiny{\href{https://www.linkedin.com/in/musharraf-rao}{https://www.linkedin.com/in/musharraf-rao}}
\end{tabular*}

\vspace{6px}

%-----------EDUCATION-----------------

\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{National University of Computer and Emerging Sciences}{}
{BS Computer Science }{2018 -- 2022}

\resumeSubHeadingListEnd


%--------SKILLS------------

\section{Skills}
\resumeSubHeadingListStart
\itemsep0em 
\item{
	\textbf{Business}{: Communication, Creativity, Leadership.}
}
\item{
	\textbf{Programming}{: Logics, OOP Concepts, Data Structure.}
}
\item{
	\textbf{Management}{: Time Management, Flexibility.}
}

\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------

\section{Technical Skills}
\resumeSubHeadingListStart
\itemsep0em 
\item{
	\textbf{Programming}{: Python, Java, C++.}
}

\item{
	\textbf{Web}{: Node.js, Flask, HTML, CSS.}
}
\item{
	\textbf{Libraries}{: Pandas, Numpy.}
}
\item{
	\textbf{Databases}{: MySQL, SQL.}
}
\item{
	\textbf{Data visualization}{: Kiali.}
}
\item{
	\textbf{Network Monitoring}{: XDP, eBPF, Cisco Packet Tracer.}
}
\item {
	\textbf{Operating System}{: Linux, Kali, Windows}
}

\item{
	\textbf{Cloud} {: Docker, Kubernetes, Istio.}
}


\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------

\section{Work Experience}
\resumeSubHeadingListStart

\resumeSubheading
{Final Year Project}{}
{Software Developer}{Feb 2022 - Present}
\resumeItemListStart
\resumeItem{Development Assistance - Blockchain Application:}
{Developing a Block-chain-based decentralized framework for Appraisal system. We enhanced the flexibility of Appraisal System by smart  contract. A series of design algorithms based on smart contract were proposed to construct a concrete scheme under the framework.we evaluated our approach on Ethereum Virtual Machine by implementing components providing decentralized Appraisal services.}
\resumeItemListEnd

\resumeSubheading
{FAST-NUCES}{}
{Student}{Jul 2018 - Jul 2022}
\resumeItemListStart
\resumeItem{Fake News Detection:}
{The primary aim of this Project is to identify patterns in text that differentiate fake articles from true news. Applied machine learning algorithms like K-Nearest Neighbors (KNN), Logistic Regression and Random Forest (RF).}
\resumeItem{Packet Filtering:}
{Purpose was to filter all unwanted packets as early as possible, so the filtering mechanism had to be shifted from user space utilities like tcpdump to the in-kernel virtual machine. This was done by using eBPF(Berkeley Packet Filter), XDP(Express Data Path) and Linux CLI.}
\resumeItem{Wifi Password Security:}
{This Project done by using Kali Linux Command and Wireshark and Aircrack- ng which is a complete suite of tools to assess wifi network security.}
\resumeItem{Voting System:}
{Develop a web application of voting system by using Flask, Html, CSS, MySQl, Python, Bootstrap and than containerized by docker and kubernetes.}
\resumeItem{Online Shopping System:}
{Develop a web application of Online Shopping System by using NodeJS, Html, CSS, SQl and React Native.}
\resumeItem{Library Management System:}
{Develop a simple Program of library management system by using OPP concepts, Programming Skills, C++ and SQl.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------Language-----------------

\section{Language}
\resumeSubHeadingListStart
\itemsep0em 
\item{
	\textbf{}{English}
}
\item{
	\textbf{}{Urdu}
}

\resumeSubHeadingListEnd


\end{document}\\
